Performing and evaluating graph-based clustering with rOpenScPCA

### 2024-11-13 analyses/hello-clusters/01_perform-evaluate-clustering.Rmd
one seed to rule them all, and fix yaml

---
title: "Performing and evaluating graph-based clustering with rOpenScPCA"
date: `r Sys.Date()`
author: Data Lab
params:
  seed: 2024
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
    df_print: paged
---

@@

@@

We also strongly recommend providing a random seed with the `seed` argument to ensure reproducibility.

```{r cluster sce}
# Calculate clusters with default parameters
cluster_results <- calculate_clusters(
  sce,
  seed = params$seed
)

@@

We also strongly recommend providing a random seed with the `seed` argument to ensure reproducibility.

```{r cluster seurat}
cluster_results <- calculate_clusters(
  seurat_obj,
  # Since we converted this from an SCE object, its PC name is `PCA`
  pc_name = "PCA",
  seed = params$seed
)

>>>>

---
title: "Performing and evaluating graph-based clustering with rOpenScPCA"
date: "`r Sys.Date()`"
author: Data Lab
params:
  seed: 2024
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
    df_print: paged
---

@@

### Set the random seed

Because clustering involves random samples, it is important to set the random seed at the top of your analysis script or notebook to ensure reproducibilty.

```{r set seed}
set.seed(params$seed)
```

@@

```{r cluster sce}
# Calculate clusters with default parameters
cluster_results <- calculate_clusters(sce)

@@

```{r cluster seurat}
cluster_results <- calculate_clusters(
  seurat_obj,
  # Since we converted this from an SCE object, its PC name is `PCA`
  pc_name = "PCA"
)
